```{r}
source(here::here("src", "setup.R"), echo = FALSE)
```

<!---------------------------------------------------------->
<!---------------------------------------------------------->
# I. Data
***

```{r}
(supplementary_data <- load_supplementary_data())
```

```{r}
(vasc_data <- load_pcr_data(target = "vasc", reprocess = TRUE))
```

<!---------------------------------------------------------->
<!---------------------------------------------------------->
# II. Model fitting
***

Let's define the model we will fit to each `Gene`'s `DCq` data. 

Here, we will fit a simple Linear Model, which is largely similar to running a t-test between both conditions:

```{r}
vasc_model <- function(data) {
  glmmTMB(dcq ~ condition, family = gaussian("identity"), data = data, contrasts = list(condition = "contr.sum"))
}
```

Now, let's fit said model to each `Gene`'s data, for a given `Stage` and `Layer`:

```{r}
compute_fold_change <- function(mod) {
  return(
    get_data(mod)
    |> select(condition, dcq)
    |> pivot_wider(names_from = condition, values_from = dcq, values_fn = mean)
    |> summarize(fold = 2**(-1 * (IH - N)))
    |> pull(fold)
  )
}
```

```{r}
(vasc_data$models <- vasc_data$clean
  |> group_split(stage, gene)
  |> map_dfr(
    \(d) summarize(d, mod = pick(condition, dcq) |> vasc_model() |> list(), .by = c(stage, gene)), 
    .progress = "Fitting models:"
  )
  |> filter(!has_na_coefs(mod)) # Removing models that did not fit properly
  |> mutate(fold = map_dbl(mod, compute_fold_change)) # Adding the Fold change
  |> select(stage, gene, fold, mod)
)
```

<!---------------------------------------------------------->
<!---------------------------------------------------------->
# III. Model analysis
***

## Predictions

For each model we fit, we can then extract the CI and p_value for the relevant contrasts, and use those to establish if a `Gene` was up or down-regulated:

```{r}
get_emmeans_data <- function(mod) {
  return(
    emmeans(mod, specs = "condition", type = "response")
    |> contrast(method = "pairwise", adjust = "none", infer = TRUE)
    |> as.data.frame()
    |> pivot_wider(names_from = contrast, values_from = estimate)
    |> select(last_col(), LCB = lower.CL, UCB = upper.CL, p_value = p.value)
    |> mutate(across(where(is.character), \(x) na_if(x, "NaN")))
  )
}
```

```{r}
(vasc_data$predictions <- vasc_data$models
  |> group_split(stage, gene)
  |> map_dfr(\(d) mutate(d, get_emmeans_data(mod[[1]])), .progress = "Extracting model predictions:")
  |> filter(!is.na(p_value))
  |> mutate(expression = get_regulation_type(fold, p_value))
  |> select(stage, gene, fold, expression, matches("-|/"), LCB, UCB, p_value)
)
```

## Gene regulation timeline

To get a better idea of how each `Gene`'s regulation changes through time, we can plot a timeline of their expression, split by `Layer` and `Pathway`.

```{r fig.width = 12, fig.height = 8}
(
  vasc_data$predictions 
  |> left_join(supplementary_data$gene_data$ref, join_by(gene))
  |> filter(p_value <= .05)
  |> select(stage, gene, fold, p_value, expression, pathway, effect)
  |> mutate(effect = case_when(
      str_detect(expression, "Downregulated") & effect == "Pro" ~ "Anti",
      str_detect(expression, "Downregulated") & effect == "Anti" ~ "Pro",
      .default = effect
    )
  )
  |> make_fold_timeline_plot(facet_rows = "pathway", color_by = "effect", size_boost = 1.5)
  |> save_png("vasc_timeline", subfolder = "PCR")
)
```

## Temporo-functional heatmap

```{r fig.height = 8, fig.width = 15}
heatmap_data <- vasc_data$predictions |>
  filter(p_value <= .05) |>
  left_join(supplementary_data$gene_data$fx, by = "gene", relationship = "many-to-many") |>
  select(stage, gene, fold, p_value, fx, effect, abb) |> 
  mutate(tile_label = paste(round(fold, 2), stars.pval(p_value), sep = " "))

heatmap_plot <- make_heatmap(heatmap_data, xaxis = "gene", yaxis = "abb", facet = "stage") + 
  labs(x = "Gene", y = "Function") + 
  facet_grid(rows = vars(stage), scales = "free_y", space = "free_y")

save_png(heatmap_plot, "vasc_heatmap", subfolder = "PCR", height = 8, width = 15)
```

With effects:

```{r fig.height = 12, fig.width = 16}
heatmap_data_effect <- vasc_data$predictions |>
  filter(p_value <= .05) |>
  left_join(supplementary_data$gene_data$fx, by = "gene", relationship = "many-to-many") |>
  select(stage, gene, fold, p_value, fx, effect, abb) |> 
  mutate(
    tile_label = paste(
      round(fold, 2), 
      stars.pval(p_value), 
      ifelse(effect == "positive", "➕", "➖"), 
      sep = " "
    )
  )

heatmap_plot_effect <- make_heatmap(heatmap_data_effect, xaxis = "gene", yaxis = "abb", facet = "stage") + 
  labs(x = "Gene", y = "Function", caption = "➕ Positive effect | ➖ Negative effect")  + 
  facet_grid(rows = vars(stage), scales = "free_y", space = "free_y") +
  theme(plot.caption = element_text(hjust = 0.5, vjust = 0.5, face = "bold", size = 16))

save_png(heatmap_plot_effect, "vasc_heatmap_effect", subfolder = "PCR", height = 12, width = 16)
```
