```{r}
source("../../src/setup.R", echo = FALSE)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# I. Data:
***

```{r}
(vasc <- load_vasc_data())

vasc_P4 <- list(data = purrr::modify_tree(vasc$data, leaf = \(x) filter(x, stage == "P4")))
vasc_P8 <- list(data = purrr::modify_tree(vasc$data, leaf = \(x) filter(x, stage == "P8")))
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# II. Volume
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

```{r}
vasc_data_normal_small <- vasc_P4$data$normal |>
  mutate(volume = volume / 1e6, cerebellar_volume = cerebellar_volume / 1e6) |>
  mutate(mouse = factor(mouse), condition = factor(condition, levels = c("N", "IH")))

mod_vol_vasc_gauss <- glmmTMB(
  volume ~ condition * level + offset(log(cerebellar_volume)) + (1 | mouse),
  family = gaussian("log"),
  data = vasc_data_normal_small |> filter(level == "Superf"),
  REML = TRUE
)

cli_h1("[Parameters]")
parameters(mod_vol_vasc_gauss)
cli_h1("[Fitness]")
performance(mod_vol_vasc_gauss)
```

**Gamma:**

```{r}
mod_vol_vasc_gamma <- glmmTMB(
  volume ~ condition * level + offset(log(cerebellar_volume)) + (1 | mouse),
  family = Gamma("log"),
  data = vasc_P4$data$normal,
  REML = TRUE
)

cli_h1("[Parameters]")
parameters(mod_vol_vasc_gamma)
cli_h1("[Fitness]")
performance(mod_vol_vasc_gamma)
```



<!------------------------------------------------------------------------------>
## 2. Model Diagnostics
***

### Residual diagnostics

```{r fig.width = 10}
check_model(mod_vol_vasc_gamma)

make_acf_plot(mod_vol_vasc_gamma)
```


### Predictive checks

```{r}
mod_vol_vasc_gamma_dharma <- DHARMa::simulateResiduals(mod_vol_vasc_gamma, plot = FALSE, n = 300, seed = getOption("seed"))
mod_vol_vasc_gamma_dharma_t <- t(mod_vol_vasc_gamma_dharma$simulatedResponse)
```

```{r fig.width = 10}
ppc_plots(mod_vol_vasc_gamma, simulations = mod_vol_vasc_gamma_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P8_mod_Vol_PC, simulations = Calb_P8_mod_Vol_PC_dharma_t, term = "Condition")
```



<!------------------------------------------------------------------------------>
## 3. Model Analysis
***

### Model parameters

**All effects (Wald):**

```{r}
parameters(
  mod_vol_vasc_gamma, exponentiate = should_exp(mod_vol_vasc_gamma),
  ci_method = "Wald", p_adjust = "none", summary = TRUE, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(mod_vol_vasc_gamma, type = 3)
```


### Marginal means

```{r}
cli_h1("[Observed]")

distribution_summary(get_data(mod_vol_vasc_gamma), dvs = find_response(mod_vol_vasc_gamma), between = "Condition")

cli_h1("[Emmeans]")

emmeans(mod_vol_vasc_gamma, specs = "Condition", type = "response")
```


### Contrasts

```{r}
cli_h1("[Link scale]")

emmeans(Calb_P8_mod_Vol_PC, specs = "Condition", type = "response") |> 
  contrast(method = "pairwise", adjust = "none", infer = TRUE)

cli_h1("[Response scale]")

emmeans(Calb_P8_mod_Vol_PC, specs = "Condition", regrid = "response") |>
  contrast(method = "pairwise", adjust = "none", infer = TRUE)
```


Plot:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(mod_vol_vasc_gamma, xaxis = "condition", subtitle = "P4") |>
  save_png("mod_vol_vasc_gamma_P4")
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(mod_vol_vasc_gamma, pred1 = "condition", pred2 = "level") |> 
  save_png("mod_vol_vasc_gamma_inter_P4")
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# III. Network Length
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# IV. Surface Area
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# V. Branchpoints
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VI. Endpoints
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VII. Number of Segments
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VIII. Segment Partitioning
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# IX. Mean Segment Radius
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**


