```{r}
source("../../src/setup.R", echo = FALSE)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# I. Data:
***

```{r}
(vasc <- load_vasc_data())

vasc_responses <- c(
  "volume",
  "network_length",
  "surface_area",
  "branchpoints",
  "endpoints",
  "number_of_segments",
  "segment_partitioning",
  "mean_segment_radius",
  "mean_segment_length",
  "mean_segment_tortuosity",
  "mean_segment_volume",
  "mean_segment_surface_area"
)

vasc_predictors <- c(
  "condition",
  "stage",
  "level",
  "mouse",
  "cerebellar_area",
  "cerebellar_volume"
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# II. Volume
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

```{r}
# test <- vasc$data$normal |> 
#   mutate(volume = volume / 1e6, cerebellar_volume = cerebellar_volume / 1e6) |> 
#   mutate(mouse = factor(mouse), condition = factor(condition, levels = c("N", "IH")))

mod_vol_vasc_gauss <- glmmTMB(
  volume ~ condition + offset(log(cerebellar_volume)) + (1 | mouse),
  family = gaussian("log"),
  data = vasc$data$normal,
  REML = TRUE
)

cli_h1("[Parameters]")
parameters(mod_vol_vasc_gauss)
cli_h1("[Fitness]")
performance(mod_vol_vasc_gauss)
```

**Gamma:**

```{r}
mod_vol_vasc_gamma <- glmmTMB(
  volume ~ condition + offset(log(cerebellar_volume)) + (1 | mouse),
  family = Gamma("log"),
  data = vasc$data$normal,
  REML = TRUE
)

cli_h1("[Parameters]")
parameters(mod_vol_vasc_gamma)
cli_h1("[Fitness]")
performance(mod_vol_vasc_gamma)
```


<!------------------------------------------------------------------------------>
## 2. Model Diagnostics
***

**Model comparison:**

```{r}
compare_performance(Calb_P8_mod_Vol_PC_gauss, Calb_P8_mod_Vol_PC_gamma)
```

Best model:

```{r}
Calb_P8_mod_Vol_PC <- Calb_P8_mod_Vol_PC_gamma
```


### Residual diagnostics

```{r fig.width = 10}
check_model(Mod_Vol_Vasc_gamma)

make_acf_plot(Mod_Vol_Vasc_gamma)
```


### Predictive checks

```{r}
Mod_Vol_Vasc_gamma_dharma <- DHARMa::simulateResiduals(Mod_Vol_Vasc_gamma, plot = FALSE, n = 300, seed = getOption("seed"))
Mod_Vol_Vasc_gamma_dharma_t <- t(Mod_Vol_Vasc_gamma_dharma$simulatedResponse)
```

```{r fig.width = 10}
ppc_plots(Calb_P8_mod_Vol_PC, simulations = Calb_P8_mod_Vol_PC_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P8_mod_Vol_PC, simulations = Calb_P8_mod_Vol_PC_dharma_t, term = "Condition")
```

### Potential outliers

```{r}
get_model_based_outliers(Calb_P8_data$clean, Calb_P8_mod_Vol_PC, Calb_P8_mod_Vol_PC_dharma, Calb_P8_responses)
```


<!------------------------------------------------------------------------------>
## 3. Model Analysis
***

### Model parameters

**All effects (Wald):**

```{r}
parameters(
  Mod_Vol_Vasc_gamma, exponentiate = should_exp(Mod_Vol_Vasc_gamma),
  ci_method = "Wald", p_adjust = "none", summary = TRUE, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Mod_Vol_Vasc_gamma, type = 3)
```


### Marginal means

```{r}
cli_h1("[Observed]")

distribution_summary(get_data(Mod_Vol_Vasc_gamma), dvs = find_response(Mod_Vol_Vasc_gamma), between = "Condition")

cli_h1("[Emmeans]")

emmeans(Mod_Vol_Vasc_gamma, specs = "Condition", type = "response")
```


### Contrasts

```{r}
cli_h1("[Link scale]")

emmeans(Calb_P8_mod_Vol_PC, specs = "Condition", type = "response") |> 
  contrast(method = "pairwise", adjust = "none", infer = TRUE)

cli_h1("[Response scale]")

emmeans(Calb_P8_mod_Vol_PC, specs = "Condition", regrid = "response") |>
  contrast(method = "pairwise", adjust = "none", infer = TRUE)
```


Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Mod_Vol_Vasc, xaxis = "Condition", subtitle = unique(Vasc_data$Stage))
```



<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# III. Network Length
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# IV. Surface Area
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# V. Branchpoints
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VI. Endpoints
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VII. Number of Segments
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# VIII. Segment Partitioning
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# IX. Mean Segment Radius
***

<!------------------------------------------------------------------------------>
## 1. Models
***

**Gaussian:**


